\cvsection{Experience}
\begin{cventries}
  \cventry
    {Designed and developed a water quality measuring device.}
    {Junior Design}
    {Durango, CO}
    {Dec. 2016 - Exp. Apr. 2016}
    {
      \begin{cvitems}
        \item {Implemented an interchangeable sensor device with a protective outer cover.}
        \item {The implemented device could measure termperature, ORP, pH, time, and GPS location.}
        \item {Role: MATLAB data analysis and LaTeX documentation.}
      \end{cvitems}
    }
    
  \cventry
    {Assembled an X-ray imaging system for two dimensional analysis of sprays.}
    {Purdue University}
    {West Lafayette, IN}
    {May. 2016 - Exp. Aug. 2016}
    {
      \begin{cvitems}
        \item {Operated spray pressure vessels, X-ray tube sources, and high-speed cameras.}
      \end{cvitems}
    }
    
  \cventry
    {Designed and develped a torsional test stand for measuring displacement.}
    {Senior Design}
    {Durango, CO}
    {Sep. 2016 - Exp. Apr. 2017}
    {
      \begin{cvitems}
        \item {Torsional test stand is capable of measuring down to 5 microns.}
        \item {Force measurements are possible in with future improvement.}
        \item {Role: MATLAB data analysis and LaTeX documentation.}
      \end{cvitems}
    }
    
  \cventry
    {Wrote tool with Python and Bash scripts.}
    {University of Wisconsin-Madison}
    {Madison, WI}
    {May. 2017 - Exp. Aug. 2017}
    {
      \begin{cvitems}
        \item {Automated image generation via VisIt.}
      \end{cvitems}
    }

  \cventry
    {}
    {Tutor and Teaching Assistant}
    {}
    {}
    {
      \begin{cvitems}
        \item {TA: Thermal and Fluid Systems Laboratory}
        \item {Tutor: Engineering Fundamentals II}
      \end{cvitems}
    }
  \cventry
    {}
    {Computer Software}
    {}
    {}
    {
      \begin{cvitems}
        \item {OS: Linux}
        \item {Drawing: AutoCAD}
        \item {Documentation: LaTeX}
        \item {Scripting: MATLAB and Python}
      \end{cvitems}
    }

\end{cventries}
